Mainstreaming Scientific Racism

### 2022-11-05 talk/talk.qmd
tweak thresholds and counting in topics over time

- "a bounded, enclosed media space that has the potential to both magnify the messages delivered within it and [insulate them from rebuttal]{.red}" [@JamiesonEchoChamberRush2008 76]

[**Did Pioneer and *Mankind Quarterly* nurture race science by protecting it from mainstream peer review?**]{}

@@

## Corpus {}

@@

::: {.column width="40%"}
- Statistical method for clustering documents and words simultaneously
- [Can we identify a race science topic?]{.red}
- [Does this topic start in MQ, spread to mainstream journals?]{.red}
:::
::::

@@

- *MQ* was the primary venue for one form of race science
	- Anthropological? 
- While mainstream journals were the primary venues for a distinct form of race science
	- *Psychological Reports*, later *Intelligence* and *PID*
	- Psychological? 
- "The race science is coming from inside the house!"

>>>>

::: {.incremental}
- "a bounded, enclosed media space that has the potential to both magnify the messages delivered within it and [insulate them from rebuttal]{.red}" [@JamiesonEchoChamberRush2008 76]
:::

[**Did Pioneer and *Mankind Quarterly* nurture race science by protecting it from mainstream peer review?**]{.fragment}\
[**Our analysis indicates *MQ* did not play this role**]{.fragment .red}

@@

## Text-mining corpus

@@

::: {.column width="40%"}
- Statistical method for clustering documents and words simultaneously

- [Can we identify a race science topic?]{.blue}
- [Does this topic start in MQ, spread to mainstream journals?]{.blue}
:::
::::

@@

- *MQ* was the primary venue for one form of race science
	- "Anthropology-flavored"? 
- While mainstream journals were the primary venues for a distinct form of race science
	- *Psychological Reports*, later *Intelligence* and *PID*
	- "Psychology-flavored"? 
- "The race science is coming from inside the house!"
